Evaluation of clustering parameters - SCPCS000170

### 2024-08-07 analyses/cell-type-wilms-tumor-06/01-clustering_SCPCS000169.Rmd
add 01-clustering abalysis

---
title: "Evaluation of clustering parameters - SCPCS000168"
author: maud-p
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S %Z")`'
output:
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: kable
params:
  sample_name: ~
  sample_path: ~
  out_rds_path: ~
---

@@

In this notebook, we will set up parameters in the seurat workflow [normalization --> reduction --> clustering] for one Wilms tumor sample (SCPCS000168) of the Wilms Tumor dataset (SCPCP000006).

@@

```{r paths2}
## to be modified when rendered
i = 1
filedir <- filelist[i] 
sample <- gsub(paste0(data_dir, "/"), "", filedir)

@@

Here we have a sample of anaplastic histology, untreated. Few thoughts:

- We thus expect anaplasia-associated patterns (TP53, MYCN as an example) to be major driver here.

@@

- We do not expect chemotherapy induced DNA damages, but maybe some DNA-repair pathways up in anaplstic cells.

@@

@@

@@

```{r fig.width=25, fig.height=5, out.width='100%'}
 SCpubr::do_ViolinPlot(srat, features = rownames(srat)[rownames(srat) %in% (CellType_metadata$ENSEMBL_ID[CellType_metadata$cell_class %in% c("malignant")])] , ncol = 9, group.by = "seurat_clusters", legend.position = "none") 
```
All clustersexcept C13 are IGF2+ (ENSG00000167244).

```{r fig.width=20, fig.height=5, out.width='100%'}
d1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
d2 <- SCpubr::do_FeaturePlot(srat, features = "ENSG00000167244", pt.size = 0.2) + ggtitle("IGF2")
v <- SCpubr::do_ViolinPlot(srat, features = "ENSG00000167244", ncol = 1, group.by = "seurat_clusters", legend.position = "none")

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
The set of clusters 0-1-4-8-9-11-12 is NCAM1+ (ENSG00000149294), which is a blastemal marker.

@@

All clusters except of C13 are WT1+ (ENSG00000184937).

```{r fig.width=20, fig.height=5, out.width='100%'}
d1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
d2 <- SCpubr::do_FeaturePlot(srat, features = "ENSG00000184937", pt.size = 0.2) + ggtitle("WT1")
v <- SCpubr::do_ViolinPlot(srat, features = "ENSG00000184937", ncol = 1, group.by = "seurat_clusters", legend.position = "none")

C10 is positive for COL6A3 which is a marker of stroma Wilms tumor cells (also normal stroma)

@@

C13 is PTPRC+ (ENSG00000081237) and must be a cluster of immune cells. Wilms tumor are generally cold tumor, especially untreated Wilms tumor. According to the clinical data, the present sample is untreated (treatment = upfront resection). We do not expect high percentage of immune cells. The size of the cluster would therefore make sense.

@@

The set of clusters 8-11 is EPCAM+ (ENSG00000119888), which is a marker of epithelial (malignant and normal) kidney cells.

```{r fig.width=20, fig.height=5, out.width='100%'}
d1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
d2 <- SCpubr::do_FeaturePlot(srat, features = "ENSG00000119888", pt.size = 0.2) + ggtitle("EPCAM")
v <- SCpubr::do_ViolinPlot(srat, features = "ENSG00000119888", ncol = 1, group.by = "seurat_clusters", legend.position = "none")

@@

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
"Normal" cells (immune, C13) have a slightly higher TP53 score.

@@

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
I am not sure how relevant the DNA repair score is. To be tested on more samples.

@@

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
Not sure what to do with these scores.

@@

PTPRC (C13, CD45), define the immune cluster.

@@

```{r fig.width=25, fig.height=6, out.width='100%'}
tmp_H <- NULL
for(i in unique(srat$seurat_clusters)){
signature = s.markers$feature[s.markers$group1 == i]
ego_module <- enricher(gene = signature, universe = background, TERM2GENE = msigdbr_hallmarks)
tmp <- NULL

@@

MYC enrichment is expected in anaplastic samples.

@@

@@

- C10 is enriched in adulte differentiated cell types/pathway of the kidney.
This could suggest that C10 are from normal kidney. 
To be checked with inferCNV profile.

- C2, C5are enriched in muscle pathways, suggesting a stromal origin.

@@

Even if the result of SingleR and CellAssign are not specific to a Wilms tumor dataset, it give the first impression that C13 a cluster of immune cells.

@@

# Preprocess with SCTransform
# Note, the RunAzimuth change a bit the Seurat object, changing for example the rownames to Symbol. 
# We thus choose to rename the object to keep the 
data <-  RunAzimuth(srat, ref_dir, assay = 'RNA')
rm(reference)
gc()

DT::datatable(table(data$seurat_clusters, data$predicted.compartment), caption = ("table of azimuth compartment annotation per seurat clusters"),               extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
              buttons = c( 'csv', 'excel')))

DT::datatable(table(data$seurat_clusters, data$predicted.celltype), caption = ("table of azimuth annotation per seurat clusters"), 
              extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
              buttons = c( 'csv', 'excel')))

@@

d1 <- DimPlot(data, reduction = "umap", group.by = "seurat_clusters", label = TRUE) + NoLegend()
d2 <- DimPlot(data, reduction = "umap", dims = c(1,2), group.by = "predicted.compartment", label = TRUE, repel = TRUE) + NoLegend()
d3 <- DimPlot(data, reduction = "umap", dims = c(1,2), group.by = "predicted.celltype", label = TRUE, repel = TRUE) + NoLegend()

@@

Looking at the predicted cell types, we observed that most of the clusters are labeled as cap mesenchyme, an early developmental stage of nephron.
This suggest that these clusters are either blastema or primitive epithelium.

@@

f1 <- SCpubr::do_BarPlot(sample = data,
                         group.by = "predicted.compartment",
                         split.by = "seurat_clusters",
                         position = "fill",
                         font.size = 10,
                         legend.ncol = 3) +
                         ggtitle("% cells")+
                         xlab(file)

f2 <- SCpubr::do_BarPlot(sample = data,
                         group.by = "predicted.celltype",
                         split.by = "seurat_clusters",
                         position = "fill",
                         font.size = 10,
                         legend.ncol = 3) +
                         ggtitle("% cells")+
                         xlab(file)

@@

- C13 = immune cells (with high confidency)

- C10, is composed of stroma (normal or cancer) cells and endothelium cells. Might be a cluster of normal cells, a bit mixed. To be checked with inferCNV.

- the two other set of clusters are cancer cells, with positivity for some Wilms tumor markers such as NCAM, WT1, EPCAM.

>>>>

---
title: "Evaluation of clustering parameters - SCPCS000169"
author: maud-p
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S %Z")`'
output:
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: kable
params:
  sample_name: ~
  sample_path: ~
  out_rds_path: ~
---

@@

In this notebook, we will set up parameters in the seurat workflow [normalization --> reduction --> clustering] for one Wilms tumor sample (SCPCS000169) of the Wilms Tumor dataset (SCPCP000006).

@@

```{r paths2}
## to be modified when rendered
i = 2
filedir <- filelist[i] 
sample <- gsub(paste0(data_dir, "/"), "", filedir)

@@

Here we have a sample of favorable histology, untreated. Few thoughs:

- We thus do not expect anaplasia-associated patterns (TP53 as an example) to be major driver here.

@@

- We do not expect chemotherapy induced DNA damages.

@@

The umap clustering is expected for a triphasic Wilms tumor sample. The 3 main clusters might be:

- blastema cancer cells
- epithelium cancer and/or normal cells
- stroma cancer and/or normal cells

The two small clusters C11 and C12 might be immune and endothelial cells.

To be checked in the following analysis!

@@

C1 might be composed of cycling cells, in higher proportion than the other clusters.

@@

```{r fig.width=25, fig.height=5, out.width='100%'}
 SCpubr::do_ViolinPlot(srat, features = rownames(srat)[rownames(srat) %in% (CellType_metadata$ENSEMBL_ID[CellType_metadata$cell_class %in% c("malignant")])] , ncol = 9, group.by = "seurat_clusters", legend.position = "none") 
```
The set of clusters 0-1-3-4-7-9-10-13 is NCAM1+ (ENSG00000149294) which is a marker of blastema area.

@@

C2-7 is positive for COL6A3 which is a marker of stroma Wilms tumor cells (also normal stroma)

@@

C11 is PTPRC+ (ENSG00000081237) and must be a cluster of immune cells. Wilms tumor are generally cold tumor, especially untreated Wilms tumor. According to the clinical data, the present sample is untreated (treatment = upfront resection). We do not expect high percentage of immune cells. The size of the cluster would therefore make sense.

@@

C12 is VWF+ (ENSG00000110799) and must be a cluster of endothelial cells.

```{r fig.width=20, fig.height=5, out.width='100%'}
d1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
d2 <- SCpubr::do_FeaturePlot(srat, features = "ENSG00000110799", pt.size = 0.2) + ggtitle("VWF")
v <- SCpubr::do_ViolinPlot(srat, features = "ENSG00000110799", ncol = 1, group.by = "seurat_clusters", legend.position = "none", pt.size = 2)

@@

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
"Normal" cells (immune, endothelial) have a slightly higher TP53 score. I am however not sure how relevant the TP53 score is for Favorable sample as the one we are analysing here. To be tested on an anaplastic sample.

@@

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
I am not sure how relevant the DNA repair score is for Favorable sample as the one we are analysing here. To be tested on an anaplastic sample.

@@

C10 might have a slightly altered DROSHA/DICER1 ratio compared to the other cluster, but this might be due to the fact that C10 is mostly in G2M phase (?).

@@

UNC5D (C0, dependency receptor), has been described in cancer and shown to regulate p53-dependent apoptosis (https://pubmed.ncbi.nlm.nih.gov/24691657/). We know that especially in blastema cell, p53 signaling play an important role.

PDCH7 (C6, protocadherin 7) is expressed in human kidney renal tubule (normal kidney epithelium, see https://www.proteinatlas.org/ENSG00000169851-PCDH7/tissue/kidney) and has been associated with oncogenic function in lung cancer (https://pubmed.ncbi.nlm.nih.gov/30409919/, https://www.frontiersin.org/journals/pharmacology/articles/10.3389/fphar.2023.1217213/full).

EBF1 (C7, Early B Cell factor 1) has been shown to play a role in kidney development, esp. glomerular, while expressed in stroma progenitor (https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6727263/).

ERBB4 (C8, EGF receptor family) is expressed during kidney development of epithelial tubule and uteric bud (https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3269924/)

FLT1 (C12, vascular endothelial growth factor receptor 1), PCAM and ELMO1 in the top5 of C13 marker genes confirm the identification of endothelial cells (https://www.ahajournals.org/doi/pdf/10.1161/CIRCRESAHA.109.213983, https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4986701/)

@@

```{r fig.width=25, fig.height=3, out.width='100%'}
tmp_H <- NULL
for(i in unique(srat$seurat_clusters)){
signature = s.markers$feature[s.markers$group1 == i]
ego_module <- enricher(gene = signature, universe = background, TERM2GENE = msigdbr_hallmarks)
tmp <- NULL

@@

- C2 and C13 are enriched for EMT signature (Warning count = 3) which makes sense with the hypothesis that they are stroma cluster.

@@

- C5, which is though to be more epithelial, has a specific enrichment pattern of PRMD4, F10 and BCL6B targets.
Might be usefull to look more into detail in the lit. if this pattern comes more often accross other samples.

- C13 has a specific enrichement of HMGB2 targets, which is though to be associated with "stemness". 
Would makes sense with the hypothesis tht C13 is blastema.

@@

- C0 is enriched in fetal metanephric cells, which makes sense with the hypothesis that C0 is blastema.

- C2, C7 is enriched in adult kidney mesenchymal cells (interstitial, muscle and mesenglial).
As the associated pathways are from "adult" reference, this might suggests that the cells are from normal kidney. 
To be checked with inferCNV profile.

- C5, C6, C8 is enriched in adulte differentiated cell types/pathway of the kidney.
This could suggest that C5 are from normal kidney. 
To be checked with inferCNV profile.

- C12 is enriched in endothelial gene sets, which fits whith the hypothesis that C12 are endothelial cells.

@@

Even if the result of SingleR and CellAssign are not specific to a Wilms tumor dataset, it give the first impression that C12 is a cluster of endothelial cells and C11 a cluster of immune cells.

@@

# Preprocess with SCTransform
srat <-  RunAzimuth(srat, ref_dir, assay = 'RNA')
rm(reference)
gc()

DT::datatable(table(srat$seurat_clusters, srat$predicted.compartment), caption = ("table of azimuth compartment annotation per seurat clusters"),               extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
              buttons = c( 'csv', 'excel')))

DT::datatable(table(srat$seurat_clusters, srat$predicted.celltype), caption = ("table of azimuth annotation per seurat clusters"), 
              extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
              buttons = c( 'csv', 'excel')))

@@

d1 <- DimPlot(srat, reduction = "umap", group.by = "seurat_clusters", label = TRUE) + NoLegend()
d2 <- DimPlot(srat, reduction = "umap", dims = c(1,2), group.by = "predicted.compartment", label = TRUE, repel = TRUE) + NoLegend()
d3 <- DimPlot(srat, reduction = "umap", dims = c(1,2), group.by = "predicted.celltype", label = TRUE, repel = TRUE) + NoLegend()

@@

Looking at the predicted cell types, we observed that the set of cluster [0,1,3,4,9,10,14] is labeled as cap mesenchyme, an early developmental stage of nephron, while the set of clusters [2,7,13] is labeled with more differentiated epithelial units of the kidney. 
This suggest that:

- clusters [0,1,3,4,9,10,14] are more stem, either primitive epithelium or blastem cancer cells. 
- clusters [2,7,13] are more differentiated, either epithelial cancer cells or normal cells.

@@

f1 <- SCpubr::do_BarPlot(sample = srat,
                         group.by = "predicted.compartment",
                         split.by = "seurat_clusters",
                         position = "fill",
                         font.size = 10,
                         legend.ncol = 3) +
                         ggtitle("% cells")+
                         xlab(file)

f2 <- SCpubr::do_BarPlot(sample = srat,
                         group.by = "predicted.celltype",
                         split.by = "seurat_clusters",
                         position = "fill",
                         font.size = 10,
                         legend.ncol = 3) +
                         ggtitle("% cells")+
                         xlab(file)

@@

- C12 = endothelium (with high confidency)
- C11 = immune cells (with high confidency)

- C2. C7, C13, that form a unit in the umap reduction, are stromal cells, either cancer or normal (with high confidency)
- C[0-1-3-4-9-10-14] that form a unit in the umap reduction, are label as cap mesenchyme (<=> stem) and NCAM+ must be blastema cancer cells.
- C[5-6-8] that form a unit in the umap reduction, are label as epithelial cells (SingleR) and differentiated kidney epithelium subunit (Fetal kidney atlas) must be epithelial (cancer or normal)

The primary aim of this script was to assess the quality of clustering and play with clustering parameters. On this sample, we are happy with the clustering, as we could identify:

- one cluster of immune cells (cell marker PTPRC, SingleR, Azimuth label transfer fro the fetal kidney) 
- one cluster of endothelial cells (cell marker VWF, SingleR, Azimuth label transfer fro the fetal kidney)
- one set of clusters of stromal cells
- one set of cluster of epithelial cells
- one set of cluster of blastema cancer cells.

### 2024-08-07 analyses/cell-type-wilms-tumor-06/01-clustering_SCPCS000170.Rmd
add 01-clustering abalysis

---
title: "Evaluation of clustering parameters - SCPCS000168"
author: maud-p
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S %Z")`'
output:
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: kable
params:
  sample_name: ~
  sample_path: ~
  out_rds_path: ~
---

@@

In this notebook, we will set up parameters in the seurat workflow [normalization --> reduction --> clustering] for one Wilms tumor sample (SCPCS000168) of the Wilms Tumor dataset (SCPCP000006).

@@

```{r paths2}
## to be modified when rendered
i = 1
filedir <- filelist[i] 
sample <- gsub(paste0(data_dir, "/"), "", filedir)

@@

Here we have a sample of anaplastic histology, untreated. Few thoughts:

- We thus expect anaplasia-associated patterns (TP53, MYCN as an example) to be major driver here.

@@

# Normalization
options(future.globals.maxSize= 891289600)
srat <- SCTransform(srat, verbose = F, conserve.memory = TRUE)

@@

@@

```{r fig.width=25, fig.height=5, out.width='100%'}
 SCpubr::do_ViolinPlot(srat, features = rownames(srat)[rownames(srat) %in% (CellType_metadata$ENSEMBL_ID[CellType_metadata$cell_class %in% c("malignant")])] , ncol = 9, group.by = "seurat_clusters", legend.position = "none") 
```
All clustersexcept C13 are IGF2+ (ENSG00000167244).

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
The set of clusters 0-1-4-8-9-11-12 is NCAM1+ (ENSG00000149294), which is a blastemal marker.

@@

All clusters except of C13 are WT1+ (ENSG00000184937).

C10 is positive for COL6A3 which is a marker of stroma Wilms tumor cells (also normal stroma)

@@

@@

The set of clusters 8-11 is EPCAM+ (ENSG00000119888), which is a marker of epithelial (malignant and normal) kidney cells.

@@

@@

d1 + d2 + v + plot_layout(ncol = 3, widths = c(1,1,3))
```
Not sure what to do with these scores.

@@

The cluster that we found seems to make sense as they can be defined by a few number of specific genes each. I don't know most of the marker genes found, but few point below that could support the analysis and annotation.

PTPRC (C13, CD45), define the immune cluster.

@@

```{r fig.width=25, fig.height=6, out.width='100%'}
tmp_H <- NULL
for(i in unique(srat$seurat_clusters)){
signature = s.markers$feature[s.markers$group1 == i]
ego_module <- enricher(gene = signature, universe = background, TERM2GENE = msigdbr_hallmarks)
tmp <- NULL

@@

MYC enrichment is expected in anaplastic samples.

@@

- C10 is enriched in adulte differentiated cell types/pathway of the kidney.
This could suggest that C10 are from normal kidney. 
To be checked with inferCNV profile.

- C2, C5are enriched in muscle pathways, suggesting a stromal origin.

@@

Even if the result of SingleR and CellAssign are not specific to a Wilms tumor dataset, it give the first impression that C13 a cluster of immune cells.

@@

Looking at the predicted compartment, we are satisfied that the immune, endothelium and stroma compartment are specific to a set of clusters. 
It is expected that the fetal__nephron compartment match to both blastema and epithelial cancer and normal kidney. 
It is thus OK to have it labeling two distinct set of clusters.

Looking at the predicted cell types, we observed that most of the clusters are labeled as cap mesenchyme, an early developmental stage of nephron.
This suggest that these clusters are either blastema or primitive epithelium.

@@

- C13 = immune cells (with high confidency)

- C10, is composed of stroma (normal or cancer) cells and endothelium cells. Might be a cluster of normal cells, a bit mixed. To be checked with inferCNV.

- the two other set of clusters are cancer cells, with positivity for some Wilms tumor markers such as NCAM, WT1, EPCAM.

Additionally, we showed the feasibility to run label transfer using runAzimuth (part of step 3 of the proposed analysis:  https://github.com/maud-p/OpenScPCA-analysis/issues/1).

We also showed the easy and robust identification of normal cells (endothelial and immune cells) that would serve as reference for the CNV inference (inferCNV, step 4 of the analysis).

>>>>

---
title: "Evaluation of clustering parameters - SCPCS000170"
author: maud-p
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S %Z")`'
output:
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: kable
params:
  sample_name: ~
  sample_path: ~
  out_rds_path: ~
---

@@

In this notebook, we will set up parameters in the seurat workflow [normalization --> reduction --> clustering] for one Wilms tumor sample (SCPCS000170) of the Wilms Tumor dataset (SCPCP000006).

@@

```{r paths2}
## to be modified when rendered
i = 3
filedir <- filelist[i] 
sample <- gsub(paste0(data_dir, "/"), "", filedir)

@@

Here we have a sample of favorable histology, untreated. Few thoughts:

- We thus do not expect anaplasia-associated patterns (TP53 as an example) to be major driver here.

@@

# Normalization
options(future.globals.maxSize= 891289600000)
srat <- SCTransform(srat, verbose = F, conserve.memory = TRUE)

@@

C9 and C13 might be a specific subtype, immune, endothelium, healthy cells (?)

@@

```{r fig.width=25, fig.height=5, out.width='100%'}
 SCpubr::do_ViolinPlot(srat, features = rownames(srat)[rownames(srat) %in% (CellType_metadata$ENSEMBL_ID[CellType_metadata$cell_class %in% c("malignant")])] , ncol = 9, group.by = "seurat_clusters", legend.position = "none") 
```
Almost all clusters are NCAM1+ (ENSG00000149294) which is a marker of blastema area.

@@

C9 is positive for COL6A3 which is a marker of stroma Wilms tumor cells (also normal stroma)

@@

Almost all clusters are WT1+ (ENSG00000184937).

Almost all clusters are IGF2+ (ENSG00000167244).

@@

The set of clusters [0-2-3-4-5-6-11-12] is EPCAM+ (ENSG00000119888), which is a marker of epithelial (malignant and normal) kidney cells.

@@

C9 is slightly VWF+ (ENSG00000110799) and might contain few endothelial cells.

```{r fig.width=20, fig.height=5, out.width='100%'}
d1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
d2 <- SCpubr::do_FeaturePlot(srat, features = "ENSG00000110799", pt.size = 0.2) + ggtitle("VWF")
v <- SCpubr::do_ViolinPlot(srat, features = "ENSG00000110799", ncol = 1, group.by = "seurat_clusters", legend.position = "none", pt.size = 2)

@@

@@

- PAX8 (C2), associated woth blastema and epithelial tumor cells (https://pubmed.ncbi.nlm.nih.gov/34306127/)
- CD74 and HLA-DRA in C3 suggest the presence of immune cells in C13.

@@

```{r fig.width=25, fig.height=7, out.width='100%'}
tmp_H <- NULL
for(i in unique(srat$seurat_clusters)){
signature = s.markers$feature[s.markers$group1 == i]
ego_module <- enricher(gene = signature, universe = background, TERM2GENE = msigdbr_hallmarks)
tmp <- NULL

@@

- C9 is enriched for EMT signature (Warning count = 5) which makes sense with the hypothesis that they are stroma cluster.

@@

@@

Even if the result of SingleR and CellAssign are not specific to a Wilms tumor dataset, we can say that C13 a cluster of immune cells.

@@

Looking at the predicted compartment, we are satisfied that the immune compartment is specific to C13. 
Endothelium and stroma compartment are mixed in C9.

It is expected that the fetal__nephron compartment match to both blastema and epithelial cancer and normal kidney.

Looking at the predicted cell types, we observed that the set of cluster [0,1,2,3,4,5,6,7,8,10,11,12] is labeled as cap mesenchyme, an early developmental stage of nephron
This suggest that clusters [0,1,2,3,4,5,6,7,8,10,11,12] are more stem, either primitive epithelium or blastem cancer cells.

@@

- C9 = stroma + endothelium (with high confidency)
- C13 = immune cells (with high confidency)

- C2. C7, C13, that form a unit in the umap reduction, are stromal cells, either cancer or normal (with high confidency)
- [0,1,2,3,4,5,6,7,8,10,11,12] are cancer cells, either blastema or primitive epithelium.
